Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States \\ \vspace{10mm} \small{Markus Neumann, Fridolin Linder, Bruce Desmarais \\ Department of Political Science - Penn State University}

### 2018-09-12 paper/TADA2018_Poster/stmTopWords60.tex
poster for TADA

\begingroup\scriptsize

@@

   30 & \cellcolor{white}fort & \cellcolor{white}thence & \cellcolor{white}blvd & \cellcolor{white}worth & \cellcolor{white}ave & \cellcolor{white}west & \mybar{681} \\ 
   58 & \cellcolor{white}councilor & \cellcolor{white}auburn & \cellcolor{white}plain & \cellcolor{white}ward & \cellcolor{white}beech & \cellcolor{white}glen & \mybar{480} \\ 
   51 & \cellcolor{white}whereas & \cellcolor{white}councilman & \cellcolor{white}alderman & \cellcolor{white}ordain & \cellcolor{white}hereby & \cellcolor{white}resolution & \mybar{420} \\ 
   16 & \cellcolor{white}recreation & \cellcolor{white}park & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{682} \\ 
   36 & \cellcolor{white}retiree & \cellcolor{white}retirement & \cellcolor{white}actuarial & \cellcolor{white}deductible & \cellcolor{white}dental & \cellcolor{white}pension & \mybar{470} \\ 
   27 & \cellcolor{white}exam & \cellcolor{white}incumbent & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}examination & \cellcolor{white}knowledge & \mybar{687} \\ 
   56 & \cellcolor{white}historic & \cellcolor{white}landmark & \cellcolor{white}revival & \cellcolor{white}archaeological & \cellcolor{white}century & \cellcolor{white}historian & \mybar{2587} \\ 
   12 & \cellcolor{white}parking & \cellcolor{white}hotel & \cellcolor{white}garage & \cellcolor{white}space & \cellcolor{white}retail & \cellcolor{white}square & \mybar{321} \\ 
   41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}abatement & \cellcolor{white}real & \cellcolor{white}estate & \cellcolor{white}property & \mybar{310} \\ 

@@

\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 

>>>>

\begingroup\footnotesize

@@

   %30 & \cellcolor{white}fort & \cellcolor{white}thence & \cellcolor{white}blvd & \cellcolor{white}worth & \cellcolor{white}ave & \cellcolor{white}west & \mybar{681} \\ 
   %58 & \cellcolor{white}councilor & \cellcolor{white}auburn & \cellcolor{white}plain & \cellcolor{white}ward & \cellcolor{white}beech & \cellcolor{white}glen & \mybar{480} \\ 
   %51 & \cellcolor{white}whereas & \cellcolor{white}councilman & \cellcolor{white}alderman & \cellcolor{white}ordain & \cellcolor{white}hereby & \cellcolor{white}resolution & \mybar{420} \\ 
   %16 & \cellcolor{white}recreation & \cellcolor{white}park & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{682} \\ 
   %36 & \cellcolor{white}retiree & \cellcolor{white}retirement & \cellcolor{white}actuarial & \cellcolor{white}deductible & \cellcolor{white}dental & \cellcolor{white}pension & \mybar{470} \\ 
   %27 & \cellcolor{white}exam & \cellcolor{white}incumbent & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}examination & \cellcolor{white}knowledge & \mybar{687} \\ 
   %56 & \cellcolor{white}historic & \cellcolor{white}landmark & \cellcolor{white}revival & \cellcolor{white}archaeological & \cellcolor{white}century & \cellcolor{white}historian & \mybar{2587} \\ 
   %12 & \cellcolor{white}parking & \cellcolor{white}hotel & \cellcolor{white}garage & \cellcolor{white}space & \cellcolor{white}retail & \cellcolor{white}square & \mybar{321} \\ 
   %41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}abatement & \cellcolor{white}real & \cellcolor{white}estate & \cellcolor{white}property & \mybar{310} \\ 

@@

%\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
